---
always_allow_html: yes
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "man/figures/README-"
)

```

# pliman <img src="man/figures/logo_pliman.svg" align="right" height="140/"/>

<!-- badges: start -->

[![CRAN status](https://www.r-pkg.org/badges/version-ago/pliman)](https://CRAN.R-project.org/package=pliman) [![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental-1) ![Total Downloads](https://cranlogs.r-pkg.org/badges/grand-total/pliman) [![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/last-month/pliman?color=orange)](https://r-pkg.org/pkg/pliman) [![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/last-week/pliman?color=orange)](https://r-pkg.org/pkg/pliman) [![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/last-day/pliman?color=orange)](https://r-pkg.org/pkg/pliman) [![DOI](https://zenodo.org/badge/352844585.svg)](https://zenodo.org/badge/latestdoi/352844585)

<!-- badges: end -->

The pliman (**pl**ant **im**age **an**alysis) package is designed to analyze plant images, particularly for leaf and seed analysis. It offers a range of functionalities to assist with various tasks such as measuring disease severity, counting lesions, obtaining lesion shapes, counting objects in an image, extracting object characteristics, performing Fourier Analysis, obtaining RGB values, extracting object coordinates and outlines, isolating objects, and plotting object measurements.

`pliman` also provides useful functions for image [transformation](https://tiagoolivoto.github.io/pliman/reference/utils_transform.html), [binarization](https://tiagoolivoto.github.io/pliman/reference/image_binary.html), [segmentation](https://tiagoolivoto.github.io/pliman/reference/image_segment.html), and [resolution](https://tiagoolivoto.github.io/pliman/reference/utils_dpi.html). Please, visit the [Examples](https://tiagoolivoto.github.io/pliman/index.html) page in `pliman` website for a detailed documentation of each function.

# Installation

Install the latest stable version of `pliman` from [CRAN](https://CRAN.R-project.org/package=pliman) with:

```{r, eval=FALSE}
install.packages("pliman")

```

The development version of `pliman` can be installed from [GitHub](https://github.com/TiagoOlivoto/pliman) with:

```{r, eval=FALSE}
devtools::install_github("TiagoOlivoto/pliman")

# To build the HTML vignette use
devtools::install_github("TiagoOlivoto/pliman", build_vignettes = TRUE)

```

*Note*: If you are a Windows user, you should also first download and install the latest version of [Rtools](https://cran.r-project.org/bin/windows/Rtools/).

# Basic usage

## Analyze objects

The function `analyze_objects()` can be used to analyze objects such as leaves, grains, pods, and pollen in an image. The following example counts and computes several features of soybean grains of an image with 30 grains.

```{r}
library(pliman)
img <-image_pliman("soybean_touch.jpg", plot = TRUE)
soy <- analyze_objects(img, marker = "id")
str(soy$results)
```

# Disease severity

## Using image indexes

To compute the percentage of symptomatic leaf area you can use the `measure_disease()` function you can use an image index to segment the entire leaf from the background and then separate the diseased tissue from the healthy tissue. Alternatively, you can provide color palette samples to the `measure_disease()` function. In this approach, the function fits a general linear model (binomial family) to the RGB values of the image. It then uses the color palette samples to segment the lesions from the healthy leaf.

In the following example, we compute the symptomatic area of a soybean leaf. The proportion of healthy and symptomatic areas is given as a proportion of the total leaf area after segmenting the leaf from the background (blue).

```{r}
img <- image_pliman("sev_leaf.jpg")
# Computes the symptomatic area
measure_disease(img = img,
                index_lb = "B", # to remove the background
                index_dh = "NGRDI", # to isolate the diseased area
                threshold = c("Otsu", 0), # You can also use the Otsu algorithm in both indexes (default)
                plot = TRUE)
```

## Interactive disease measurements

An alternative approach to measuring disease percentage is available through the `measure_disease_iter()` function. This function offers an interactive interface that empowers users to manually select sample colors directly from the image. By doing so, it provides a highly customizable analysis method.

One advantage of using `measure_disease_iter()` is the ability to utilize the "mapview" viewer, which enhances the analysis process by offering zoom-in options. This feature allows users to closely examine specific areas of the image, enabling detailed inspection and accurate disease measurement.

```{r eval=FALSE}
img <- image_pliman("sev_leaf.jpg", plot = TRUE)
measure_disease_iter(img, viewer = "mapview")
```



# Citation

```{r, comment=""}
citation("pliman")
```

# Getting help

If you come across any clear bugs while using the package, please consider filing a minimal reproducible example on [github](https://github.com/TiagoOlivoto/pliman/issues). This will help the developers address the issue promptly.

Suggestions and criticisms aimed at improving the quality and usability of the package are highly encouraged. Your feedback is valuable in making {pliman} even better!

# Code of Conduct

Please note that the pliman project is released with a [Contributor Code of Conduct](https://tiagoolivoto.github.io/pliman/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

::: {align="center"}
<a href='https://www.free-website-hit-counter.com'><img src="https://www.free-website-hit-counter.com/c.php?d=9&amp;id=144207&amp;s=2" alt="Free Website Hit Counter" border="0"/></a><br/><small><a href='https://www.free-website-hit-counter.com' title="Free Website Hit Counter">Free website hit counter</a></small>
:::
