---
always_allow_html: yes
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "man/figures/README-"
)

```

# pliman <img src="man/figures/logo_pliman.svg" align="right" height="140/"/>

<!-- badges: start -->

<!-- [![CRAN status](https://www.r-pkg.org/badges/version-ago/metan)](https://CRAN.R-project.org/package=metan) [![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable) ![Downloads](http://cranlogs.r-pkg.org/badges/metan) ![Total Downloads](https://cranlogs.r-pkg.org/badges/grand-total/metan) [<img src="https://zenodo.org/badge/130062661.svg" alt="DOI" width="186"/>](https://zenodo.org/badge/latestdoi/130062661) -->

<!-- badges: end -->

`pliman` (**pl**ant **im**age **an**anlysis) is designed to analyze plant images, especially related to leaf analysis. You provide color palettes, tell `pliman` what each one represents, and it takes care of the details. The package will help you to:

* Measure leaf area
* Measure disease severity
* Count the number of lesions

# Installation

The development version of `pliman` can be installed from [GitHub](https://github.com/TiagoOlivoto/pliman) with:

```{r, eval=FALSE}
devtools::install_github("TiagoOlivoto/pliman")

# To build the HTML vignette use
devtools::install_github("TiagoOlivoto/pliman", build_vignettes = TRUE)

```

*Note*: If you are a Windows user, you should also first download and install the latest version of [Rtools](https://cran.r-project.org/bin/windows/Rtools/).


# Usage
# Disease severity

```{r fig.width=12, fig.height=3}
library(pliman)
img <- image_import(system.file("tmp_images/sev2.png", package = "pliman"))
healthy <- image_import(system.file("tmp_images/sev_healthy.png", package = "pliman"))
symptoms <- image_import(system.file("tmp_images/sev_sympt.png", package = "pliman"))
background <- image_import(system.file("tmp_images/sev_back.png", package = "pliman"))
image_combine(img, healthy, symptoms, background, ncol = 4)

```

```{r}
symptomatic_area(img = img,
                 img_healthy = healthy,
                 img_symptoms = symptoms,
                 img_background = background,
                 show_image = TRUE)
```

# Count crop grains
The function `count_objects()` can be used to count the grains of an image. In the following example, we will count the number of soybean grains of an image with 150 grains.

```{r}
img <- image_import(system.file("tmp_images/soy_150.png", package = "pliman"))
image_show(img)
count_objects(img)

```

In the following example, we will enumerate the grains with an area greater than the mean of all grains in the image and add a white background to the processed image.

```{r}
count_objects(img,
              show_segmentation = FALSE,
              col_background = "white",
              marker = "text",
              lower_size = 611.92,
              marker_size = 0.5,
              marker_col = "black")
```


# Getting help

-   If you encounter a clear bug, please file a minimal reproducible example on [github](https://github.com/TiagoOlivoto/pliman/issues)

-   Suggestions and criticisms to improve the quality and usability of the package are welcome!
