---
always_allow_html: yes
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "man/figures/README-"
)

```

# pliman <img src="man/figures/logo_pliman.svg" align="right" height="140/"/>

<!-- badges: start -->

<!-- [![CRAN status](https://www.r-pkg.org/badges/version-ago/metan)](https://CRAN.R-project.org/package=metan) [![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable) ![Downloads](http://cranlogs.r-pkg.org/badges/metan) ![Total Downloads](https://cranlogs.r-pkg.org/badges/grand-total/metan) [<img src="https://zenodo.org/badge/130062661.svg" alt="DOI" width="186"/>](https://zenodo.org/badge/latestdoi/130062661) -->

<!-- badges: end -->

`pliman` (**pl**ant **im**age **an**anlysis) is designed to analyze plant images, especially related to leaf analysis. You provide color palettes, tell `pliman` what each one represents, and it takes care of the details. The package will help you to:

* Measure leaf area
* Measure disease severity
* Count the number of lesions

# Installation

The development version of `pliman` can be installed from [GitHub](https://github.com/TiagoOlivoto/metan) with:

```{r, eval=FALSE}
devtools::install_github("TiagoOlivoto/metan")

# To build the HTML vignette use
devtools::install_github("TiagoOlivoto/metan", build_vignettes = TRUE)

```

*Note*: If you are a Windows user, you should also first download and install the latest version of [Rtools](https://cran.r-project.org/bin/windows/Rtools/).


# Usage


```{r fig.width=12, fig.height=3}
library(pliman)
img <- import_image(system.file("tmp_images/sev2.png", package = "pliman"))
healthy <- import_image(system.file("tmp_images/sev_healthy.png", package = "pliman"))
symptoms <- import_image(system.file("tmp_images/sev_sympt.png", package = "pliman"))
background <- import_image(system.file("tmp_images/sev_back.png", package = "pliman"))
combine_images(img, healthy, symptoms, background, ncol = 4)

```

```{r}
symptomatic_area(img = img,
                 img_healthy = healthy,
                 img_symptoms = symptoms,
                 img_background = background,
                 show_image = TRUE)
```


# Getting help

-   If you encounter a clear bug, please file a minimal reproducible example on [github](https://github.com/TiagoOlivoto/pliman/issues)

-   Suggestions and criticisms to improve the quality and usability of the package are welcome!
