---
always_allow_html: yes
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "man/figures/README-"
)

```

# pliman <img src="man/figures/logo_pliman.svg" align="right" height="140/"/>

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version-ago/pliman)](https://CRAN.R-project.org/package=pliman)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental-1)
![Total Downloads](https://cranlogs.r-pkg.org/badges/grand-total/pliman)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/last-month/pliman?color=orange)](https://r-pkg.org/pkg/pliman)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/last-week/pliman?color=orange)](https://r-pkg.org/pkg/pliman)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/last-day/pliman?color=orange)](https://r-pkg.org/pkg/pliman)
[![DOI](https://zenodo.org/badge/352844585.svg)](https://zenodo.org/badge/latestdoi/352844585)
<!-- badges: end -->

`pliman` (**pl**ant **im**age **an**alysis) is designed to analyze plant images, especially related to leaf analysis. You provide color palettes, tell `pliman` what each one represents, and it takes care of the details. Image indexes can also be used to segment images. The package will help you to:

* Measure leaf area;
* Measure disease severity;
* Count the number of lesions;
* Obtain the shape of lesions;
* Produce Standard Area Diagrams;
* Count objects in an image;
* Get object features (area, perimeter, radius, circularity, eccentricity, solidity);
* Get the RGB values for each object in an image;
* Get the object coordinates;
* Get the object contours;
* Get convex hulls;
* Isolate objects;
* Plot object measures;
* Perform Elliptical Fourier Analysis;
* 


`pliman` also provides useful functions for image [transformation](https://tiagoolivoto.github.io/pliman/reference/utils_transform.html), [binarization](https://tiagoolivoto.github.io/pliman/reference/image_binary.html), [segmentation](https://tiagoolivoto.github.io/pliman/reference/image_segment.html), and [resolution](https://tiagoolivoto.github.io/pliman/reference/utils_dpi.html). Please, visit the [Examples](https://tiagoolivoto.github.io/pliman/index.html) page in `pliman` website for a detailed documentation of each function.


# Installation

Install the latest stable version of `pliman` from [CRAN](https://CRAN.R-project.org/package=pliman) with:

```{r, eval=FALSE}
install.packages("pliman")

```

The development version of `pliman` can be installed from [GitHub](https://github.com/TiagoOlivoto/pliman) with:

```{r, eval=FALSE}
devtools::install_github("TiagoOlivoto/pliman")

# To build the HTML vignette use
devtools::install_github("TiagoOlivoto/pliman", build_vignettes = TRUE)

```

*Note*: If you are a Windows user, you should also first download and install the latest version of [Rtools](https://cran.r-project.org/bin/windows/Rtools/).


# Basic usage
The two main functions of pliman are `analyze objects()` and `measure disease()`, which can be used to compute object features and measure disease severity, respectively.

## Analyze objects
The function `analyze_objects()` can be used to analyze objects such as leaves, grains, pods, and pollen in an image. The following example counts and computes several features of soybean grains of an image with 30 grains.

```{r}
library(pliman)
img <-image_pliman("soybean_touch.jpg", plot = TRUE)
soy <- analyze_objects(img, marker = "id")
str(soy$results)
```

## Disease severity

```{r fig.width=12, fig.height=3}
img <-image_pliman("sev_leaf.jpg")
healthy <-image_pliman("sev_healthy.jpg")
symptoms <-image_pliman("sev_sympt.jpg")
background <-image_pliman("sev_back.jpg")
image_combine(img, healthy, symptoms, background, ncol = 4)

```

```{r}
sev <- 
  measure_disease(img = img,
                  img_healthy = healthy,
                  img_symptoms = symptoms,
                  img_background = background)

sev$severity
```

`pliman` takes the advantage of several powerful functions from [EBImage package](https://bioconductor.org/packages/release/bioc/html/EBImage.html). Thanks to Andrzej Oleś and collaborators for the impressive job done with EBImage!


# Citation

```{r, comment=""}
citation("pliman")
```



# Getting help

-   If you encounter a clear bug, please file a minimal reproducible example on [github](https://github.com/TiagoOlivoto/pliman/issues). The package [reprex](https://reprex.tidyverse.org/) may help you with that.

-   Suggestions and criticisms to improve the quality and usability of the package are welcome!

# Code of Conduct

Please note that the pliman project is released with a [Contributor Code of Conduct](https://tiagoolivoto.github.io/pliman/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.



<div align='center'><a href='https://www.free-website-hit-counter.com'><img src='https://www.free-website-hit-counter.com/c.php?d=9&id=144207&s=2' border='0' alt='Free Website Hit Counter'></a><br/><small><a href='https://www.free-website-hit-counter.com' title="Free Website Hit Counter">Free website hit counter</a></small></div>


