---
always_allow_html: yes
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "man/figures/README-"
)

```

# pliman <img src="man/figures/logo_pliman.svg" align="right" height="140/"/>

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version-ago/pliman)](https://CRAN.R-project.org/package=metan)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#experimental)
![Downloads](http://cranlogs.r-pkg.org/badges/pliman)
![Total Downloads](https://cranlogs.r-pkg.org/badges/grand-total/pliman)
[![DOI](https://zenodo.org/badge/352844585.svg)](https://zenodo.org/badge/latestdoi/352844585)
<!-- badges: end -->

`pliman` (**pl**ant **im**age **an**alysis) is designed to analyze plant images, especially related to leaf analysis. You provide color palettes, tell `pliman` what each one represents, and it takes care of the details. Image indexes can also be used to segment images. The package will help you to:

* Measure leaf area with `leaf_area()`
* Measure disease severity with `symptomatic_area()`
* Count the number of lesions with `count_lesions()`
* Count objects in an image with `count_objects()`
* Get the RGB values for each object in an image with `objects_rgb()`
* Get object measures with `get_measures()`
* Plot object measures with `plot_measures()`

`pliman` also provides useful functions for [operation](https://tiagoolivoto.github.io/pliman/reference/image_combine.html), [transformation](https://tiagoolivoto.github.io/pliman/reference/utils_transform.html), and [segmentation](https://tiagoolivoto.github.io/pliman/reference/image_binary.html) of images. Please, visit the [Examples](https://tiagoolivoto.github.io/pliman/index.html) page in `pliman` website for a detailed documentation of each function.


# Installation

The development version of `pliman` can be installed from [GitHub](https://github.com/TiagoOlivoto/pliman) with:

```{r, eval=FALSE}
devtools::install_github("TiagoOlivoto/pliman")

# To build the HTML vignette use
devtools::install_github("TiagoOlivoto/pliman", build_vignettes = TRUE)

```

*Note*: If you are a Windows user, you should also first download and install the latest version of [Rtools](https://cran.r-project.org/bin/windows/Rtools/).


# Basic usage
# Disease severity

```{r fig.width=12, fig.height=3}
library(pliman)
img <- image_import(image_pliman("sev_leaf.jpg"))
healthy <- image_import(image_pliman("sev_healthy.jpg"))
symptoms <- image_import(image_pliman("sev_sympt.jpg"))
background <- image_import(image_pliman("sev_back.jpg"))
image_combine(img, healthy, symptoms, background, ncol = 4)

```

```{r}
symptomatic_area(img = img,
                 img_healthy = healthy,
                 img_symptoms = symptoms,
                 img_background = background,
                 show_image = TRUE)
```

# Count objects
The function `count_objects()` can be used to count the objects such as leaves, grains, pods, pollen in an image. In the following example, we will count the number of soybean grains of an image with 30 grains.

```{r}
img <- image_import(image_pliman("soybean_touch.jpg"))
image_show(img)
count_objects(img, marker = "text")

```


`pliman` takes the advantage of several powerful functions from [EBImage package](https://bioconductor.org/packages/release/bioc/html/EBImage.html). Thanks to Andrzej Oleś and collaborators for the impressive job done with EBImage!


# Getting help

-   If you encounter a clear bug, please file a minimal reproducible example on [github](https://github.com/TiagoOlivoto/pliman/issues)

-   Suggestions and criticisms to improve the quality and usability of the package are welcome!

# Code of Conduct

Please note that the pliman project is released with a [Contributor Code of Conduct](https://tiagoolivoto.github.io/pliman/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

