---
title: "Count objects in an image"
author: "Tiago Olivoto"
date: "`r Sys.Date()`"
always_allow_html: yes
output: rmarkdown::html_vignette
fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Count objects in an image}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  rmarkdown.html_vignette.check_title = FALSE,
  fig.width = 10
)
```

# Getting started

The function `count_objects()` can be used to count objects in an image. Let us start with a simple example with the image `object_300dpi.png` available in the [GitHub page](https://github.com/TiagoOlivoto/pliman/tree/master/image_examples). To facilitate the image importation from this folder, a helper function `image_pliman()` is used.

```{r}
library(pliman)
img <- image_import(image_pliman("objects_300dpi.jpg"))
image_show(img)
```

The above image was produced with Microsoft Power Point. It has a known resolution of 300 dpi (dots per inch) and shows four objects

-   Larger square: 10 x 10 cm (100 cm^2^)
-   Smaller square: 5 x 5 cm (25 cm^2^)
-   Rectangle: 4 x 2 cm (8 cm^2^)
-   Circle: 3 cm in diameter (\~7.08 cm^2^)

To count the objects in the image we use `count_objects()` and inform the image object (the only mandatory argument). First, we use `image_binary()` to see the most suitable index to segment the objects from background. By default, the R, G, B (first row) and their normalized values (second row) are used.

```{r}
image_binary(img)
img_res <- 
  count_objects(img,
                marker = "text", # identify objects
                index = "B") # use blue index to segment

```

# Getting the object measures

The results were stored in `img_res` and a summary print in the console. The minimum, mean, maximum, standard deviation and sum of pixels are given for both area, and perimeter. The values for each object can be obtained with `get_measures()`. Since there is no scale declared in the above example, we have no idea about the actual area of the objects in cm^2^, only in pixels.

```{r}
(measures <- get_measures(img_res))
image_show(img)
text(measures$x, measures$y, measures$id)
```

# Adjusting object measures

There are two main ways of adjusting the object measures (from pixels to cm, for example). The first one is to declare the known area, perimeter, or radius of a given object. The measure for the other objects will be then computed by a simple rule of three. The second one, is by declaring a known image resolution in dpi (dots per inch). In this case, the perimeter, area and radius will be adjusted by the informed dpi. 

## Declaring a known value 
Since we have known the area of the larger square (object 1), let us adjust the area of the other objects in the image using that.

```{r}
get_measures(img_res,
             id = 1,
             measure = "area",
             true_value = 100)
```

The same can be used to adjust the measures based on the perimeter or radius. Let us adjust the perimeter of objects by the perimeter of object 2 (20 cm).

```{r}
get_measures(img_res,
             id = 2,
             measure = "perimeter",
             true_value = 20)
```

## Declaring the image resolution

If the image resolution is known, all the measures will be ajusted according to this resolution. Let us to see a numerical example with `pixels_to_cm()`. This function converts the number of pixels ($px$) to cm, considering the image resolution in $dpi$, as follows: $cm = px \times (2.54/dpi)$. We known that the larger square has a perimeter of 4720 pixels. So, using the function we have

```{r}
pixels_to_cm(px = 4720, dpi = 300)

```
The perimeter of the object 1 adjusted by the image resolution is very close to the true (40 cm). Bellow, the values of all measures are adjusted by declaring the `dpi` argument in `get_measures()`.

```{r}
get_measures(img_res, dpi = 300)
```


# Counting crop grains 

Here, we will count the grains in the image `soybean_touch.png`. This image has a cyan background and contains 50 soybean grains that don't touch with each other. Two segmentation strategies are used. The first one is by using is image segmentation based on color indexes. 

```{r}
soy <-        image_import(image_pliman("soybean_touch.jpg"))
grain <-      image_import(image_pliman("soybean_grain.jpg"))
background <- image_import(image_pliman("background.jpg"))
image_combine(soy, grain, background, ncol = 3)
```

## Image segmentation
### Getting image indexes
`pliman` provides a set of indexes that can be used to segment images. For a list of supported indexes consult the documentation of `image_index()` function. Here, we use the argument `index"` to test the segmentation based on the RGB and their normalized values. The results are shown in the plot according to the order of the indexes in the `index` argument, filled 'by row'. User can also provide your own index with the argument `my_index`.

```{r }
indexes <- image_index(soy, index = c("R, G, B, NR, NG, NB"))
```

```{r}
# Create a histogram with the RGB values
plot(indexes)
```


### Producing a segmented image

The function `image_segmentation()` is used to segment images using image indexes. In our example, we will use the same indexes computed below to see how the image is segmented. The output of this function can be used as input in the function `count_objets()`.

```{r}
segmented <- image_segment(soy, index = c("R, G, B, NR, NG, NB"))

```

It seems that the "NB" index provided better segmentation. "R" and "NR" resulted in an inverted segmented image, i.e., the grains were considered as background and the remaining as 'selected' image. To circumvent this problem, we can use the argument `invert` in those functions.


### Producing a binary image

We can also produce a binary image with `image_binary()`. Just for curiosity, we will use the indexes `"R"` and `"NB"`.

```{r}
binary <- image_binary(soy, index = c("R, NB"))

```


## Count the grains in the image
### Using image indexes
The function `count_objects()` segment the image using as default the normalized blue index, as follows $NB = (B/(R+G+B))$, where $R$, $G$, and $B$ are the red, green, and blue bands. Objects are count and the segmented objects colored with random permutations.

```{r}
count <- 
  count_objects(soy,
                index = "NB") # default

```

Users can remove the random coloration and identify the objects (in this example the grains) by using the arguments `marker = "text"` and `show_segmentation = FALSE`. The color of the background can also be changed with `col_background`.

```{r}
count <- 
  count_objects(soy,
                marker = "text",
                show_segmentation = FALSE,
                col_background = "white",
                index = "NB") # default
```

```{r}
# Get the object measures
(measures <- get_measures(count))
```

In the following example, we will select objects with an area above the average of all objects by using `lower_size = 2051.9667`. Additionally, we will use the argument `show_original = FALSE` to show the results as colors (non-original image).

```{r}
count_objects(soy,
              marker = "text",
              show_original = FALSE,
              show_segmentation = FALSE,
              lower_size = 2051.9667,
              index = "NB") # default
```

Users can also select the top `n` objects based on either smaller or largest areas. Let's see how to point out the 5 grains with the smallest area, showing the original grains in a blue background. We will also use the argument `my_index` to choose a personalized index to segment the image. Just for comparison, we will set up explicitly the normalized blue index by calling `my_index = "B/(R+G+B)"`.

```{r}
count_objects(soy,
              marker = "point",
              show_segmentation = FALSE,
              topn_lower = 5,
              col_background = "blue",
              my_index = "B/(R+G+B)") # default
```


### Using sample palettes

Sometimes it is difficult to choose an image index that segments the image efficiently (even using `my_index` ). In `pliman` users have an alternative image segmentation strategy that is using sample color palettes. In this case, users can say to `count_objects` which color palettes are to be used for background and foreground. A generalized linear model (binomial family) is then used to predict the value of each pixel (background or foreground). Let's see how the grains of the above image can be count with this strategy.

```{r}
count_objects(img = soy,
              background = background,
              foreground = grain)
```


Provided that the images are stored in the current working directory (or subdirectory), users can count the objects with no need to first import the image into the R environment. In this case, image names need to be declared as characters. Assuming that soy, background, and grain are the images saved into the current working directory, the same result as above is obtained with

```{r eval=FALSE}
count_objects(img = "soy",
              background = "background",
              foreground = "grain")
```

# Batch processing


