---
title: "Image manipulation with pliman"
author: "Tiago Olivoto"
date: "`r Sys.Date()`"
always_allow_html: yes
output: rmarkdown::html_vignette
fig_caption: yes
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  rmarkdown.html_vignette.check_title = FALSE
)
```


# Image manipulation

## Importing images 

```{r import1 }
library(pliman)
soy <- image_pliman("soybean_touch.jpg")
```


To import a list of images, the argument `pattern` of the function `image_import()` is used. All images that match the pattern name are imported into a list.

```{r import2 }
soy_list <- 
  image_import(pattern = "sev_",
               path = image_pliman()) # choose path directory
names(soy_list)
```




## Displaying images 
Single images are displayed with `plot()`. For combining images, the function `image_combine()` is used. Users can inform either a comma-separated list of objects or a list of objects of class `Image`.

```{r display1, fig.width=12, fig.height=6}
# Single images
plot(soy)


```



```{r display2, fig.width=12, fig.height=6}
# Combine images
image_combine(soy, soy)

# Combine images
image_combine(soy_list, ncol = 5)

```


## Manipulating images


`pliman` provides a set of `image_*()` functions to perform image manipulation and transformation of unique images or a list of images based on the [EBImage package](https://www.bioconductor.org/packages/release/bioc/vignettes/EBImage/inst/doc/EBImage-introduction.html).

### Resize an image
Sometimes resizing of high-resolution images is needed to reduce the processing time. The function `image_resize()` is used to resize an image. The argument `rel_size` can be used to resize the image by relative size. For example, by setting `rel_size = 50` to an image of width 1280 x 720, the new image will have a size of 640 x 360. This is useful to speed up the time of analysis such as those computed with `analyze_objects()` and `measure_disease()`.

```{r manipulate1, fig.width=10, fig.height=8}
image_dimension(soy)
soy_resized <- image_resize(soy, rel_size = 50)
image_dimension(soy_resized)
```


### Crop an image
Cropping images is useful to remove noises from the image edge, as well as to reduce the size of images before processing. To crop an image, the function `image_crop()` is used. Users need to inform a numeric vector indicating the pixel range (`width` and `height`) that will be maintained in the cropped image.

```{r, fig.width=10, fig.height=8}
crop1 <-
  image_crop(soy,
             width = 55:750,
             height = 20:623,
             plot = TRUE)
```

If only `width` or `height` are informed, the image will be cropped vertically or horizontally.

```{r, fig.width=10, fig.height=8}
crop2 <-
  image_crop(soy,
             width = 55:750,
             plot = TRUE)
```

If both `width` and `height` are missing, an iterative process of image cropping is performed.

```{r eval=FALSE, fig.width=10, fig.height=8}
# only run in an iterative section
image_crop(soy)
```


Additionally, an automated cropping process can be performed. In this case, the image will be automatically cropped to the area of objects with an edge of five pixels by default.

```{r, fig.width=10, fig.height=8}
auto_crop <- image_autocrop(soy, plot = TRUE)
```


The function `image_trim()` is used to trim pixels from image edges.


```{r manipulate2, fig.width=10, fig.height=8}
# trim 50 pixels from all edges
soy_trim <- image_trim(soy, edge = 50, plot = TRUE)

# The same is achieved with
soy_trim2 <-
  image_trim(soy,
             top = 50,
             bottom = 50,
             left = 50,
             right = 50,
             plot = TRUE)

# trim 100 pixels from top and bottom
soy_trim3 <-
  image_trim(soy,
             top = 100,
             bottom = 100,
             plot = TRUE)
# trim to 5 pixels around objects' area

```




### Image resolution (DPI) {#dpi}
The function `dpi()` runs an interactive function to compute the image resolution given a known distance informed by the user. To compute the image resolution (dpi) the user must use the left button mouse to create a line of known distance. This can be done, for example, using a template with known distance in the image (e.g., `leaves.JPG`).

```{r eval=FALSE}
# only run in an interactive section
leaves <- image_import("./data/leaf_area/leaves.JPG")
dpi(leaves)
```


<iframe width="760" height="430" src="https://www.youtube.com/embed/Rh10_pLgeng" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>



### Rotate an image
`image_rotate()` is used to rotates the image clockwise by the given angle.

```{r manipulate3, fig.width=10, fig.height=8}
soy_rotated <- image_rotate(soy, angle = 45, plot = TRUE)
```


### Horizontal and vertical reflection
`image_hreflect()` and `image_vreflect()` performs vertical and horizontal reflection of images, respectively.

```{r manipulate4, fig.width=20}
soy_hrefl <- image_hreflect(soy)
soy_vrefl <- image_vreflect(soy)
image_combine(soy, soy_hrefl, soy_vrefl, ncol = 3)
```



### Horizontal and vertical conversion
`image_horizontal()` and `image_vertical()` converts (if needed) an image to a horizontal or vertical image, respectively.

```{r manipulate5, fig.width=20}
soy_h <- image_horizontal(soy)
soy_v <- image_vertical(soy)
image_combine(soy, soy_h, soy_v, ncol = 3)

```


### Filter, blur, contrast, dilatation, and erosion

```{r manipulate6, fig.width=10, fig.height=8, fig.height=6}
soy_filter <- image_filter(soy)
soy_blur <- image_blur(soy)
soy_contrast <- image_contrast(soy)
soy_dilatation <- image_dilate(soy)
soy_erosion <- image_erode(soy)
image_combine(soy, soy_filter, soy_blur, soy_contrast, soy_dilatation, soy_erosion)
```



### Exporting images
To export images to the current directory, use the function `image_export()`. If a list of images is exported, the images will be saved considering the name and extension present in the list. If no extension is present, the images will be saved as `*.jpg` files.

```{r export, eval=FALSE}
image_export(soy, "exported.jpg")
```

# <i class="fas fa-scroll"></i> A little bit more!

<!-- inicio font awesome -->
<script src="https://kit.fontawesome.com/1f72d6921a.js" crossorigin="anonymous"></script>

> At [this link](https://tiagoolivoto.github.io/paper_pliman/code.html) you will find more examples on how to use {pliman} to analyze plant images. Source code and images can be downloaded [here](https://github.com/TiagoOlivoto/paper_pliman/archive/refs/heads/master.zip). You can also find a talk (Portuguese language) about {pliman} [here](https://www.youtube.com/watch?v=ElvUVlPocgA). <i class="far fa-lightbulb"></i>Lights, <i class="fas fa-camera"></i>camera, {pliman}!
