---
title: "Image manipulation with pliman"
author: "Tiago Olivoto"
date: "`r Sys.Date()`"
always_allow_html: yes
output: rmarkdown::html_vignette
fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Image manipulation with pliman}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  rmarkdown.html_vignette.check_title = FALSE
)
```

`pliman` provides useful functions to perform image transformation of unique images or list of images based on the [EBImage package](https://www.bioconductor.org/packages/release/bioc/vignettes/EBImage/inst/doc/EBImage-introduction.html).

```{r fig.width=10}
library(pliman)
img <- image_import(image_pliman("sev_leaf_nb.jpg"))
img_neg <- max(img) - img

img_list <- list(img = img, img_neg = img_neg)
image_dimension(img_list)
image_combine(img_list)

```

# Rezise an image
`image_resize()` is used to resize an image. The argument `rel_size` can be used to resize the image by a relative size. For example, setting `rel_size = 50` to an image of width 1280 x 720, the new image will have a size of 640 x 360. This is useful to speed up the time of analysis such as those computed with `count_objects` and `symptomatic_area()`.

```{r}
resized <- image_resize(img_list, rel_size = 50)
image_dimension(resized)
```

# Rotate an image
`image_rotate()` is used to rotates the image clockwise by the given angle.

```{r fig.width=10}
rotated <- image_rotate(img_list, angle = 45)
image_combine(rotated)
```

# Horizontal and vertical reflextion
`image_hreflect()` and `image_vreflect()` performs vertical and horizontal reflection of images, respectively.

```{r fig.width=10}
img_hrefl <- image_hreflect(img)
img_vrefl <- image_vreflect(img)
image_combine(img, img_hrefl, img_vrefl, ncol = 3)
```



# Horizontal and horizontal conversion
`image_horizontal()` and `image_vertical()` converts (if needed) an image to a horizontal or vertical image, respectively.

```{r fig.width=10}
img_h <- image_horizontal(img)
img_v <- image_vertical(img)
image_combine(img, img_h, img_v, ncol = 3)

```


