---
title: "Image operations with pliman"
author: "Tiago Olivoto"
date: "`r Sys.Date()`"
always_allow_html: yes
output: rmarkdown::html_vignette
fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Image operations with pliman}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  rmarkdown.html_vignette.check_title = FALSE
)
```

# Getting started
`pliman` provides a consistent way to import, export, show and combine images.

# Importing images

Images are imported with `image_import()`. Users can indicate either a character vector of file names or URLs. Using the argument `img_pattern` several images can be imported at once, and a list of images is created. For example, if `img_pattern = "im"` all images in the current working directory that the name matches the pattern (e.g., `img1.-, image1.-, im2.-`) will be imported to a list. Providing any number as pattern (e.g., `img_pattern = "1"`) will select images that are nammed as `1.-, 2.-`, and so on.


```{r }
library(pliman)
img <- image_import(image_pliman("sev_leaf_nb.jpg"))

```

# Showing images

Images are shown with `image_show()`. The imput argument can be either an `Image` object or an array.

```{r }
image_show(img)

```


```{r}
set.seed(10)
mat <- matrix(sample(c(0, 1), 100, replace = TRUE), ncol = 10)
mat
image_show(mat)
```


# Exporting images

Images are imported with `image_export()`. In the following example, `img` will be exported as a `png` image named `my_image` in the current working directory.

```{r eval = FALSE}
image_export(img, name = "my_image.jpg")
```

