---
title: "Phytopatometry in R with the package pliman"
author: "Tiago Olivoto"
date: "`r Sys.Date()`"
always_allow_html: yes
output: rmarkdown::html_vignette
fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Phytopatometry in R with the package pliman}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  rmarkdown.html_vignette.check_title = FALSE
)
```

# Getting started


# Single images

```{r disease1, fig.width=12, fig.height=3}
library(pliman)
# set the path directory
path_soy <- "https://raw.githubusercontent.com/TiagoOlivoto/pliman/master/vignettes/imgs"
# import images
img <- image_import("leaf.jpg", path = path_soy)
healthy <- image_import("healthy.jpg", path = path_soy)
symptoms <- image_import("sympt.jpg", path = path_soy)
background <- image_import("back.jpg", path = path_soy)
image_combine(img, healthy, symptoms, background, ncol = 4)


```

# Image palettes
Sample palettes can be made by simply manually sampling small areas of representative images and producing a composite image that will represent each of the desired classes (background, healthy, and symptomatic tissues). Another way is to use the `image_palette()` function to create sample color palettes

```{r}
pals <- image_palette(img, npal = 8)
image_combine(pals, ncol = 4)
```

```{r disease2, fig.width=10, fig.height=7}
# default settings
res <-
  measure_disease(img = img,
                  img_healthy = healthy,
                  img_symptoms = symptoms,
                  img_background = background)
```

Alternatively, users can create a mask instead of showing the original image.

```{r disease3, fig.width=10, fig.height=7}

# create a personalized mask
measure_disease(img = img,
                img_healthy = healthy,
                img_symptoms = symptoms,
                img_background = background,
                show_original = FALSE, # create a mask
                show_contour = FALSE, # hide the contour line
                col_background = "white", # default
                col_lesions = "red", # default
                col_leaf = "green") # default


```


# Variations in image palettes
The results may vary depending on how palettes are chosen and are subjective due to the researcher’s experience. In the following example, I show a second example with a variation in the color palettes, where only the necrotic area is assumed to be the diseased tissue. Therefore, the symptomatic area will be smaller than the previous one.

```{r disease4, fig.width=10, fig.height=7}

# import images
healthy2 <- image_import("healthy2.jpg", path = path_soy)
symptoms2 <- image_import("sympt2.jpg", path = path_soy)
background2 <- image_import("back2.jpg", path = path_soy)
image_combine(healthy2, symptoms2, background2, ncol = 3)

img2 <- img
res <-
  measure_disease(img = img,
                  img_healthy = healthy2,
                  img_symptoms = symptoms2,
                  img_background = background2)
res$severity
```


# Lesion shape

```{r fig.width=10, fig.height=7}
res <-
  measure_disease(img = img,
                  img_healthy = healthy,
                  img_symptoms = symptoms,
                  img_background = background,
                  show_features = TRUE,
                  marker = "area")
res$shape
res$statistics
```



