---
title: "Image segmentation with pliman"
author: "Tiago Olivoto"
date: "`r Sys.Date()`"
always_allow_html: yes
output: rmarkdown::html_vignette
fig_caption: yes
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  rmarkdown.html_vignette.check_title = FALSE
)
```

# Getting started
Image segmentation is the process of partitioning a digital image into multiple segments (sets of pixels or image objects). In the context of plant image analysis, segmentation is used to simplify the representation of an image into something easier to analyze. For example, when using `count_objects()` to count crop grains, first the grains need to be isolated (segmented) from the background. In `pliman` the following functions can be used to segment an image.

In `pliman` the following functions can be used to segment an image.

* `image_binary()` to produce a binary (black and white) image
* `image_segment()` to produce a segmented image (image objects and a white background).
* `image_segment_iter()` to segment an image iteratively.

Both functions segment the image based on the value of some image index, which may be one of the RGB bands or any operation with these bands. Internally, these functions call `image_index()` to compute these indexes. The following indexes are currently available.

```{r echo=FALSE}
ind <- read.csv(file=system.file("indexes.csv", package = "pliman", mustWork = TRUE), header = T, sep = ";")
create_markdown_table <- function(data) {
  # Get column names
  headers <- colnames(data)
  
  # Create header row
  header_row <- paste("|", paste(headers, collapse = " | "), "|")
  
  # Create separator row
  separator_row <- paste("|", paste(rep("---", length(headers)), collapse = " | "), "|")
  
  # Create data rows
  data_rows <- apply(data, 1, function(row) {
    paste("|", paste(row, collapse = " | "), "|")
  })
  
  # Combine all rows
  markdown_table <- c(header_row, separator_row, data_rows)
  
  # Print the markdown table
  cat(paste(markdown_table, collapse = "\n"))
}

```


Here, I use the argument `index"` to test the segmentation based on the RGB and their normalized values. Users can also provide their own index by explicitly providing the formula. e.g., `index = "R-B"`.

```{r segmentation1 }
library(pliman)
soy <- image_pliman("soybean_touch.jpg")

```

```{r segmentation2, fig.width=10, fig.height=5}
# Compute the indexes
# Only show the first 8 to reduce the image size
indexes <- image_index(soy, index = pliman_indexes()[1:9], plot = FALSE)

# Create a raster plot with the RGB values
plot(indexes)

# Create a density plot with the RGB values
plot(indexes, type = "density")
```

In this example, we can see the distribution of the RGB values (first row) and the normalized RGB values (second row). The two peaks represent the grains (smaller peak) and the blue background (larger peak). The clearer the difference between these peaks, the better will the image segmentation.

## Segment an image

The function `image_segmentation()` is used to segment images using image indexes. In this example, I will use the same indexes computed below to see how the image is segmented. The output of this function can be used as input in the function `analyze_objects()`.

```{r segmentation3, fig.width=10, fig.height=5}
segmented <- image_segment(soy, index = c("R, G, B, NR, NG, NB"))
plot(segmented$NB)
```

It seems that the `"NB"` index provided better segmentation. `"R"` and `"NR"` resulted in an inverted segmented image, i.e., the grains were considered as background and the remaining as 'selected' image. To circumvent this problem, we can use the argument `invert` in those functions.

```{r segmentation4, fig.width=10, fig.height=5}
image_segment(soy,
              index = c("R, NR"),
              invert = TRUE)

```


## Iterative segmentation

The function `image_segment_iter()` provides an iterative image segmentation, returning the proportions of segmented pixels. This is useful when more than one segmentation procedure is needed. Users can choose how many segmentation perform, using the argument `nseg`.

```{r segmentation5}
seg_iter <- image_pliman("sev_leaf_nb.jpg", plot = TRUE)

```

Using a soybean sample leaf (above), I will use the function `image_segment_iter` to segment the diseased tissue from healthy tissue. The aim is to segment the symptoms into two classes, namely, necrosis (brown areas) and chlorosis (yellow areas), and compute the percentage of each symptom class. The `"VARI"` seems to be a suitable index to segment symptoms (necrosis and chlorosis) from healthy tissues. The `"GLI"` can be used to segment necrosis from chlorosis. Knowing this, we can now use `image_segment_iter()` explicitly indicating these indexes, as follows

```{r segmentation8, fig.width=10}

image_segment_iter(seg_iter,
                   nseg = 2, # two segmentations
                   index = c("VARI", "GLI"),
                   ncol = 3)
```

It can be observed that 30.28% of the original image were characterized as symptoms (both necrosis and chlorosis). Of out this (symptomatic area), 25.92% are necrotic areas. So 7.85% of the total area were considered as necrotic areas (30.288 $\times$ 0.2592 or 103464/1317600 $\times$ 100) and 22.43% (30.28 - 7.85 or (399075 - 103464) / 1317600 $\times$ 100) were considered as chlorotic areas.

Users can use the argument `threshold` to controls how segmentation is made. By default (`threshold = "Otsu"`), a threshold value based on Otsu's method is used to reduce the grayscale image to a binary image.   If a numeric value is informed, this value will be used as a threshold. Inform any non-numeric value different than `"Otsu"` to iteratively chosen the threshold based on a raster plot showing pixel intensity of the index. For `image_segmentation_iter()`, a vector (allows a mixed (numeric and character) type) with the same length of `nseg` can be used.

```{r segmentation9, fig.width=10}
seg_iter1 <-
  image_segment_iter(seg_iter,
                     nseg = 2, # two segmentations
                     index = c("VARI", "GLI"),
                     threshold = c(0, "Otsu"),
                     ncol = 3,
                     plot = FALSE)
seg_iter2 <-
  image_segment_iter(seg_iter,
                     nseg = 2, # two segmentations
                     index = c("VARI", "GLI"),
                     threshold = c(0.5, "Otsu"),
                     ncol = 3,
                     plot = FALSE)

image_combine(seg_iter1$images$seg1,
              seg_iter2$images$seg1)
```

Users can then set the argument `threshold` for their specific case, depending on the aims of the segmentation.


# Producing a binary image

We can also produce a binary image with `image_binary()`. Just for curiosity, we will use the indexes `"B"` (blue) and `"NB"` (normalized blue). By default, `image_binary()` rescales the image to 30% of the size of the original image to speed up the computation time. Use the argument `resize = FALSE` to produce a binary image with the original size.

```{r binary1, fig.width=10, fig.height=5}
binary <- image_binary(soy)

# original image size
image_binary(soy,
             index = c("B, NB"),
             resize = FALSE)
```



# <i class="fas fa-scroll"></i> A little bit more!

<!-- inicio font awesome -->
<script src="https://kit.fontawesome.com/1f72d6921a.js" crossorigin="anonymous"></script>

> At [this link](https://tiagoolivoto.github.io/paper_pliman/code.html) you will find more examples on how to use {pliman} to analyze plant images. Source code and images can be downloaded [here](https://github.com/TiagoOlivoto/paper_pliman/archive/refs/heads/master.zip). You can also find a talk (Portuguese language) about {pliman} [here](https://www.youtube.com/watch?v=ElvUVlPocgA). <i class="far fa-lightbulb"></i>Lights, <i class="fas fa-camera"></i>camera, {pliman}!

