---
title: "Image segmentation with pliman"
author: "Tiago Olivoto"
date: "`r Sys.Date()`"
always_allow_html: yes
output: rmarkdown::html_vignette
fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Image segmentation with pliman}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  rmarkdown.html_vignette.check_title = FALSE
)
```

# Getting started
Image segmentation is the process of partitioning a digital image into multiple segments (sets of pixels or image objects). In the context of plant image analysis, segmentation is used to simplify the representation of an image into something easier to analyze. For example, when using `count_objects()` to count crop grains, first the grains need to be isolated (segmented) from the background. In `pliman` the following functions can be used to segment an image.

* `image_binary()` to produce a binary (back and white) image
* `image_segment()` to produce a segmented image (image objects and a white background).

Both functions segment the image based on the value of some image index, which may be one of the RGB bands or any operation with these bands. Internally, these functions call `image_index()` to compute these indexes.

# Getting image indexes
`pliman` provides a set of indexes that can be used to segment images. For a list of supported indexes consult the documentation of `image_index()` function. Here, we use the argument `index"` to test the segmentation based on the RGB and their normalized values. The results are shown in the plot according to the order of the indexes in the `index` argument, filled 'by row'. Users can also provide your index with the argument `my_index`.

```{r }
library(pliman)
soy <- image_import(image_pliman("soybean_touch.jpg"))
image_show(soy)


```

```{r fig.width=10, fig.height=5}
# Compute the indexes
indexes <- image_index(soy, index = c("R, G, B, NR, NG, NB"))

# Create a histogram with the RGB values
plot(indexes)
```

In this example, we can see the distribution of the RGB values (first row) and the normalized RGB values (second row). The two peaks represent the grains (smaller peak) and the blue background (larger peak). The clearer the difference between these peaks, the better will the image segmentation.


# Producing a segmented image

The function `image_segmentation()` is used to segment images using image indexes. In our example, we will use the same indexes computed below to see how the image is segmented. The output of this function can be used as input in the function `count_objets()`.

```{r fig.width=10, fig.height=5}
segmented <- image_segment(soy, index = c("R, G, B, NR, NG, NB"))

```

It seems that the "NB" index provided better segmentation. "R" and "NR" resulted in an inverted segmented image, i.e., the grains were considered as background and the remaining as 'selected' image. To circumvent this problem, we can use the argument `invert` in those functions.

```{r fig.width=10, fig.height=5}
image_segment(soy,
              index = c("R, NR"),
              invert = TRUE)

```

# Producing a binary image

We can also produce a binary image with `image_binary()`. Just for curiosity, we will use the indexes `"R"` and `"NB"`. By default, `image_binary()` rescales the image to 30% of the size of the original image to speed up the computation time. Use the argument `resize = FALSE` to produce a binary image with the original size.

```{r fig.width=10, fig.height=5}
binary <- image_binary(soy, index = c("R, NB"))

# original image size
image_binary(soy,
             index = c("R, NB"),
             resize = FALSE)
```




